\TITLE

### 2024-08-12 paper/main.tex
update dispute and anonimity

\subsection{Dispute Resolution System}
\label{sec:dispute-resolution}
\begin{sloppypar}
Disputes are common in transactions, and systems are needed to ensure that rules and laws are followed. Traditionally, this has involved legal contracts and law enforcement. With blockchain technology, smart contracts offer a new way by putting contract details into code and enforcing them automatically~\cite{allenGovernanceBlockchainDispute2019}.
\end{sloppypar}

@@

\subsection{Example scenarios}\label{example-scenarios}
This section illustrates two key scenarios using figures to show the transitions of positions between the customer and the SP under different conditions.

@@

In the first scenario (Figure~\ref{fig:misbehaviour}), the SP attempts to misbehave by not delivering the service and consequently not publishing the Proof of Provision ($\mathrm{PoP}$) after receiving payment. If the SP fails to publish a valid $\mathrm{PoP}$ by the deadline $\mathrm{T}_\mathrm{provide}$, the customer is justified in starting a dispute. The customer is likely to win this dispute as the SP cannot prove the timely publication of $\mathrm{PoP}$. This scenario results in a neutral outcome for the customer and a disadvantageous outcome for the SP.

@@

The second scenario (Figure~\ref{fig:rational}) represents the rational and intended course of action, where both the customer and the SP follow the protocol as designed. This scenario is crucial as it demonstrates the protocol functioning optimally, leading to a fair outcome for both parties.

@@

Blockchain-based dispute resolution platforms such as Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019} offer a promising direction. These systems could employ a pool of field experts who, in the event of a dispute, would examine the proofs (e.g., $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) in a confidential, zero-knowledge context, providing verdicts without access to personal data. Expert participation and honest adjudication would be encouraged through a system of fees, stakes, and rewards.

>>>>

\subsection{Dispute Resolution System}
\label{sec:dispute-resolution}
\begin{sloppypar}
Disputes are common in transactions, and systems are needed to ensure that rules and laws are followed. Traditionally, this has involved legal contracts and law enforcement. With blockchain technology, smart contracts offer a new way by putting the details of a contract into code and enforcing it through a consensus mechanism.~\cite{allenGovernanceBlockchainDispute2019}.
\end{sloppypar}

@@

\subsection{Analyse scenarios}\label{example-scenarios}
This section illustrates two scenarios using figures to show the transitions of positions between the customer and the SP under different conditions.

@@

\paragraph{Dispute}
In the first scenario (Figure~\ref{fig:misbehaviour}), (1) the customer initialise the transaction and delivers the material to the SP, (2) who validates the materials and publish the Proof of Delivery ($\mathrm{PoD}$) on blockchain. (3) The customer validates the existence of PoD on blockchain and (4) pay for the transaction using one of the specified payment method. (5) The SP misbehaves by not delivering the service and consequently not publishing the Proof of Provision ($\mathrm{PoP}$) after having received the payment. Once the agreed deadline $\mathrm{T}_\mathrm{provide}$ pass the position moves to the Abnormal column and the customer is in disadvantage position and the SP is in advantage position. However, the customer is justified in starting a dispute, by collecting all the evidences, i.e., Proof of Delivery ($\mathrm{PoD}$) from Message Board, payment $\mathrm{recipt}$, and delivering them to the Dispute Resolution Service. The customer is likely to win this dispute as the SP cannot prove the timely publication of $\mathrm{PoP}$. This scenario results in a neutral outcome for the customer and a disadvantageous outcome for the SP.

@@

\paragraph{Agreement}
The second scenario (Figure~\ref{fig:rational}) represents the rational and intended course of action, where both the customer and the SP follow the protocol as designed. This scenario is crucial as it demonstrates the protocol functioning optimally, leading to a fair outcome for both parties.

@@

Blockchain-based dispute resolution platforms such as  Kleros~\cite{bergollaKlerosSociolegalCase2022, gudkovCrowdArbitrationBlockchain2020}, Themis~\cite{mengThemisDecentralizedEscrow2019}, Aragon Court~\cite{AragonWhitepaper2023,aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution (ODR) systems~\cite{allenGovernanceBlockchainDispute2019} offer a promising direction. These systems could employ a pool of field experts who, in the event of a dispute, would examine the smart contract, proofs ( $\mathrm{PoD}$, $\mathrm{PoP}$, payment $\mathrm{receipt}$) and providing verdicts. Expert participation and honest adjudication would be encouraged through a system of fees, stakes, and rewards. At the time of writing Kleros is the most successful protocol for the disputes resolution, claiminng to employ 716 jurors and having resolved 1645 disputes.
